---
# title: "SWMM Continuous Plots"
# author: "Rod Lammers"
# date: "5/26/2020"
output: 
  pdf_document:
    keep_tex: TRUE
    latex_engine: xelatex
mainfont: Arial
header-includes:
  \renewcommand{\thefigure}{S\arabic{figure}}
  \usepackage{float}
  \floatplacement{figure}{H}
  \setcounter{page}{46}
  \setcounter{figure}{42}
  \pretolerance=10000
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Additional Results from Continuous Simulations

## Summary plots
Summary results for each city for all three years (wet, normal, and dry) and three GSI soil types (high, medium, and low infiltration capacity). Plots show percent reduction in peak flow rates and runoff volume by event, as well as annual summaries of high pulse count, high pulse duration, % reduction in surface runoff volume, and Richards-Baker Flashiness index.

```{r echo=FALSE, warning=FALSE, message=FALSE, inlcude=FALSE}
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(zoo))
suppressPackageStartupMessages(library(tidyr))
library(swmmr)

source("~/WORK/R Functions/Plot Functions.R")
source("Storm event analysis.R")

#Cities
cities <- c("New_Orleans",
            "Atlanta",
            "Seattle",
            "Des_Moines",
            "Tampa",
            "Columbus",
            "Elko",
            "Los_Angeles",
            "Colorado_Springs")

cities2 <- stringr::str_replace(cities, "_", " ")

#Functions
get_results <- function(swmm_files, location = "Outfall"){
  
  # #Get the output discharge at the outfall
  out <- read_out(file = swmm_files, iType = 1, object_name = location,
                  vIndex = 4)
  
  return(out)
  
}

#Caculate summary stats from hydrographs
calc_stats <- function(results, soils, rains, ratio, threshold){
  data <- results[[1]][[1]]
  daily <- xts::apply.daily(data, mean)
  
  stats <- data.frame(vol = sum(data) * 0.9917, #runoff volume, ac-in / yr
                      vol_high = sum(data[data > threshold]), #runoff volume above high flow threshold, ac-in / yr
                      HPC = sum(table(cumsum(data < threshold)) > 1), #number of discrete peaks above flow threshold
                      HPD = sum(data > threshold) / 4, #duration of flow above threshold (in hours)
                      no_flow = sum(data < 0.5) / 4, #duration with essentially zero flow (<0.5 cfs) in hours
                      RBI = sum(abs(diff(data)), na.rm = TRUE) / sum(data), #Richards-Baker flashiness index
                      RBI_daily = sum(abs(diff(daily)), na.rm = TRUE) / sum(daily), #daily RBI
                      soil = soils,
                      rain = rains,
                      ratio = ratio
  )
  
  return(stats)
}

#Fix subcatchment report
fix_report <- function(y){
  nc <- ncol(y$subcatchment_runoff_summary)
  vals <- apply(y$subcatchment_runoff_summary[,nc], 1, strsplit, "\\s+")
  vals <- t(apply(do.call("rbind", do.call("rbind", vals)), 1, as.numeric))
  #drop column
  y$subcatchment_runoff_summary <- y$subcatchment_runoff_summary[,-nc]
  #Bind
  y$subcatchment_runoff_summary <- cbind(y$subcatchment_runoff_summary, vals)
  #Change names
  colnames(y$subcatchment_runoff_summary) <- c("Subcatchment",
                                               "Total_Precip",
                                               "Total_Runon",
                                               "Total_Evap",
                                               "Total_Infil",
                                               "Imperv_Runoff",
                                               "Perv_Runoff",
                                               "Total_Runoff_Depth",
                                               "Total_Runoff_Volume",
                                               "Total_Peak_Runoff",
                                               "Runoff_Coeff")
  
  return(y)
}

runoff_summary <- function(city, rain, soil, ratio, 
                        dir_name = "../Sims/Continuous"){
  
  #Get output
  rpt_file <- paste0(dir_name, "/", city, "/", city, "_", soil, "_", rain, "_", ratio * 100, ".rpt")
  rpt <- fix_report(read_rpt(rpt_file))
  
  #baseline output
  baseline_file <- paste0(dir_name, "/", city, "/", city, "_high_", rain, "_baseline.rpt")
  baseline_rpt <- fix_report(read_rpt(baseline_file))
  
  # #Sub-catchment results
  # input <- read_inp(stringr::str_replace(rpt_file, "rpt", "inp"))
  # 
  # comb <- left_join(rpt$subcatchment_runoff_summary, input$subcatchments, by = c("Subcatchment" = "Name")) %>%
  #   left_join(baseline_rpt$subcatchment_runoff_summary, by = "Subcatchment") %>%
  #   mutate(vol_red = ifelse(Total_Runoff_Depth.y > 0, (Total_Runoff_Depth.y - Total_Runoff_Depth.x) / Total_Runoff_Depth.y * 100, NA),
  #          peak_red = ifelse(Total_Peak_Runoff.y > 0, (Total_Peak_Runoff.y - Total_Peak_Runoff.x) / Total_Peak_Runoff.y * 100, NA))
  
  #combine into data.frame
  output <- data.frame(baseline_vol = baseline_rpt$runoff_quantity_continuity$Depth[baseline_rpt$runoff_quantity_continuity$Component 
                                                                                    == "Surface Runoff"],
                       vol = rpt$runoff_quantity_continuity$Depth[rpt$runoff_quantity_continuity$Component 
                                                                                    == "Surface Runoff"],
                       precip = rpt$runoff_quantity_continuity$Depth[rpt$runoff_quantity_continuity$Component 
                                                                                    == "Total Precipitation"],
                      #  cum_vol_red = sum(comb$vol_red * comb$Area, na.rm = TRUE) / sum(comb$Area),
                      # cum_peak_red = sum(comb$peak_red * comb$Area, na.rm = TRUE) / sum(comb$Area),
                       city = city,
                       rain = rain,
                       soil = soil) %>%
    mutate(vol_red = (baseline_vol - vol) / baseline_vol * 100)
  
  return(output)
  
}

peak_events <- function(city, rain, soil, ratio, hourly_data, threshold, location = "Outfall", subcatchments = FALSE,
                        dir_name = "../Sims/Continuous"){
  
  #Do event analysis
  index <- which(names(hourly_data) == gsub("_", " ", city))
  events <- event_separation(data = hourly_data[[index]], city = city)
  
  #Get events for year of analysis
  event_summary <- events[[1]]
  years <- unique(event_summary$year)
  analysis_year <- case_when(rain == "Dry" ~ years[1],
                             rain == "Norm" ~ years[2],
                             rain == "Wet" ~ years[3])
  
  event_summary <- filter(event_summary, year == analysis_year)
  
  #Get output
  out_file <- paste0(dir_name, "/", city, "/", city, "_", soil, "_", rain, "_", ratio * 100, ".out")
  out <- read_out(file = out_file, iType = 1, object_name = location,
                  vIndex = 4)
  
  #baseline output
  baseline_file <- paste0(dir_name, "/", city, "/", city, "_high_", rain, "_baseline.out")
  baseline_out <- read_out(file = baseline_file, iType = 1, object_name = location,
                           vIndex = 4)
  
  #Sub-basin results
  if (subcatchments){
    input <- read_inp(stringr::str_replace(out_file, "out", "inp"))
    
    sub_results <- lapply(input$subcatchments$Name, read_out, file = out_file, iType = 0, vIndex = 4)
    baseline_sub <- lapply(input$subcatchments$Name, read_out, file = baseline_file, iType = 0, vIndex = 4)
  }
  
  #combine outputs
  event_summary <- mutate(event_summary,
                          peak_out = NA,
                          peak_baseline = NA,
                          vol_out = NA,
                          vol_baseline = NA,
                          sub_peak = NA,
                          sub_vol = NA)
  for (i in 1:nrow(event_summary)){
    start <- event_summary$start[i]
    end <- event_summary$end[i] + 6 * 60 * 60 #add 6 hours to end
    index <- paste0(start, "/", end)
    flow_out <- out[[1]][[1]][index]
    flow_baseline <- baseline_out[[1]][[1]][index]
    
    event_summary$peak_out[i] <- max(flow_out)
    event_summary$peak_baseline[i] <- max(flow_baseline)
    event_summary$vol_out[i] <- sum(flow_out)
    event_summary$vol_baseline[i] <- sum(flow_baseline)
    
    if (subcatchments){
      sub_flows <- lapply(sub_results, function(x, index){x[[1]][[1]][index]}, index = index)
      baseline_flows <- lapply(baseline_sub, function(x, index){x[[1]][[1]][index]}, index = index)
      sub_peaks <- sapply(sub_flows, max)
      baseline_peaks <- sapply(baseline_flows, max)
      baseline_peaks[baseline_peaks == 0] <- NA
      sub_vol <- sapply(sub_flows, sum)
      baseline_vol <- sapply(baseline_flows, sum)
      baseline_vol[baseline_vol == 0] <- NA
      
      event_summary$sub_peak[i] <- sum((baseline_peaks - sub_peaks) / baseline_peaks * 100 
                                     * input$subcatchments$Area, na.rm = TRUE) / sum(input$subcatchments$Area)
    
      event_summary$sub_vol[i] <- sum((baseline_vol - sub_vol) / baseline_vol * 100 
                                     * input$subcatchments$Area, na.rm = TRUE) / sum(input$subcatchments$Area)
    }
  }
  
  event_summary <- mutate(event_summary,
                          peak_red = (peak_baseline - peak_out) / peak_baseline * 100,
                          vol_red = (vol_baseline - vol_out) / vol_baseline * 100,
                          city = city,
                          soil = soil,
                          ratio = ratio,
                          rain = rain) %>%
    filter(peak_baseline > threshold)
  
  return(event_summary)
  
}

snow_stats <- function(city, rain, 
                        dir_name = "../Sims/Continuous"){
  
  #Get files
  out_file <- paste0(dir_name, "/", city, "/", city, "_high_", rain, "_baseline.out")
  rainfall <- read_out(file = out_file, iType = 3,
                  vIndex = 1)
  temp <- read_out(file = out_file, iType = 3,
                  vIndex = 0)
  
  snow <- sum(rainfall$system_variable$total_rainfall[temp$system_variable$air_temperature <= 34]) / 4 #in/hr to in
  tot_rain <- sum(rainfall$system_variable$total_rainfall) / 4 #in/hr to in
  
  return(data.frame(snow,
                    tot_rain,
                    snow_perc = snow / tot_rain * 100,
                    city = city,
                    rain = rain))
}
```

```{r echo=FALSE, fig.height=7.5, fig.width=5.5, fig.cap=paste0("Peak flow reduction (a) and runoff volume reduction (b) by event, high pulse count (c), high pulse duation (d), surface runoff volume reduction (e), and flow flashiness (RBI calculated using 15-min flow data; f) for ", cities2, ". Plots (a) and (b) show only results for high infiltration soils to improve readability."), warning=FALSE, message=FALSE, fig.align="center"}
rains <- c("Dry", "Norm", "Wet")
dir <- "C:/Users/lamme1r/Documents/SWMM_bioretention/Sims/Continuous"
soils <- c("low", "med", "high")
comb_results <- list()
snow_all <- list()
event_results_all <- list()
for (k in 1:length(cities)){
#for (k in 1){
  city <- cities[k]
  
  #Get hydrographs
  files <- lapply(rains, function(x, dir){
    y <- list.files(path = dir, pattern = ".out", full.names = TRUE)
    y <- Filter(function(z) grepl(x, z), y)
    #reorder
    y <- y[c(2, 1, 4, 3)]
  }, dir = file.path(dir, city))
  
  results <- lapply(files, function(x){
    lapply(x, get_results, location = "10yr_Detention")
  })
  
  #Get snow stats
  snow <- lapply(rains, snow_stats, city = city)
  snow_all[[k]] <- do.call("rbind", snow)
  
  #Get hyetographs
  # ppt_files <- list.files(file.path(dir, city), pattern = "PPT", full.names = TRUE)
  # ppt <- lapply(ppt_files, function(x){
  #   data <- read.table(x, header = FALSE)
  #   colnames(data) <- c("City", "Year", "Month", "Day", "Hour", "Min", "PPT")
  #   data <- data %>%
  #     mutate(dateTime = paste0(Year, "/", Month, "/", Day, " ", Hour, ":", Min),
  #            dateTime = as.POSIXct(dateTime))
  # })
  # 
  # soil_type <- c("High", "Med", "Low")
  # for (i in 1:length(results)){
  #   par(mfrow = c(2, 1), mar = c(4, 4, 2, 0.5))
  #   ymax <- max(unlist(results[[i]]))
  #   ppt_max <- max(ppt[[i]]$PPT, na.rm = TRUE)
  #   
  #   barplot(I(-PPT) ~ dateTime, ppt[[i]], border = NA, col = "black", las = 1, yaxt = "n", xaxt = "n")
  #   axis(side = 2, at = seq(0, -ppt_max, -0.5), labels = seq(0, ppt_max, 0.5))
  #   for (j in 1:length(results[[i]])){
  #     plot_results(results[[i]][[j]], ymax = ymax)
  #     
  #     title(main = paste(substr(files[[i]][[j]], nchar(files[[i]][[j]]) - 9, nchar(files[[i]][[j]]) - 7), "-", soil_type[j]))
  #   }
  #   
  # }
  
  #City summary plots
  mean_flow <- mean(sapply(results, function(x){mean(x[[1]][[1]][[1]][x[[1]][[1]][[1]] > 0])}))
  
  soils2 <- c("Baseline", rev(soils))
  ratios <- c("Baseline", rep("0.1", 3))
  stats <- list()
  
  
  for(i in 1:length(rains)){
    stats[[i]] <- list()
    for(j in 1:4){
      stats[[i]][[j]] <- calc_stats(results[[i]][[j]], soils = soils2[j], rains = rains[i], ratio = 0.1, threshold = 2 * mean_flow)
    }
  }
  
  stats_combined <- do.call("rbind", do.call("rbind", stats))
  
  
  #Summary plot showing performance across different soil types and years
  percentages <- stats_combined %>%
    group_by(rain) %>%
    mutate(vol = (first(vol) - vol) / first(vol) * 100,
              vol_high = (first(vol_high) - vol_high) / first(vol_high) * 100,
              no_flow = no_flow / 24, #convert to days
              HPC = HPC,
              HPD = HPD,
              RBI = RBI,
              HPC_red = (first(HPC) - HPC) / first(HPC) * 100,
              HPD_red = (first(HPD) - HPD) / first(HPD) * 100,
              RBI_red = (first(RBI_daily) - RBI_daily) / first(RBI_daily) * 100,
              RBI_daily = RBI_daily)
  
  events_peak <- list()
  runoff <- list()
  for (i in 1:length(rains)){
    events_peak[[i]] <- list()
    runoff[[i]] <- list()
    for (j in 1:length(soils)){
      events_peak[[i]][[j]] <- peak_events(city = city, rain = rains[i], soil = soils[j], ratio = 0.1,
                                           hourly_data = hourly_data, threshold = 2 * mean_flow, location = "10yr_Detention",
                                           subcatchments = FALSE)
      runoff[[i]][[j]] <- runoff_summary(city = city, rain = rains[i], soil = soils[j], ratio = 0.1)
    }
  }
  
  events_peak_comb <- do.call("rbind", do.call("rbind", events_peak)) %>%
    mutate(rain = factor(rain, levels = c("Dry", "Norm", "Wet"))) %>%
    mutate(soil = factor(soil, levels = c("baseline", "high", "med", "low")))
  
  runoff_combined <- do.call("rbind", do.call("rbind", runoff)) %>%
    mutate(rain = factor(rain, levels = c("Dry", "Norm", "Wet"))) %>%
    mutate(soil = factor(soil, levels = c("high", "med", "low")))
  
  comb_results[[k]] <- filter(percentages, soil != "Baseline") %>%
    left_join(runoff_combined, by = c("rain", "soil"))
  
  event_results_all[[k]] <- events_peak_comb
  
  # png(paste0("~/WORK/SWMM_Rain_Gardens/City_Analysis/", city, "/", city, "_Summary_Plot.png"), type = "cairo", units = "in",
  #     height = 5, width = 5, res = 500)
  range_red <- range(c(events_peak_comb$peak_red, events_peak_comb$vol_red))
  range_red[1] <- max(range_red[1], -100) #make sure min y value doesn't go below -100%
  colors <- RColorBrewer::brewer.pal(n = 3, "PuBu")
  colors <- c("gray20", rev(colors))
  palette(cRamp_legend(3, "PuBu", alpha = 0.7))
  par(mfrow = c(3, 2), mar = c(4, 4, 1, 0.5), oma = c(1, 0, 3, 1.5), mgp = c(2.5, 0.8, 0))
  #Plot peak and volume reduction only for high infiltration soils so you can see the points
  plot(peak_red ~ I(vol * 2.54), events_peak_comb[events_peak_comb$soil == "high",], pch = 16, col = 3, las = 1, 
       ylab = "% Peak Flow Reduction", 
       ylim = range_red, xaxt = "n", xlab = "", xaxt = "n")
  mtext(side = 1, "Storm Depth", line = 3.1, xpd = NA, cex = 0.7)
  add_label(0.85, 0.05, "(a)")
  xvals <- axis(side = 1, mgp = c(2, 0.5, 0))
  axis(side = 1, at = round(xvals / 2.54) * 2.54, labels = round(xvals / 2.54), mgp = c(2, 0.5, 0), line = 1.7)
  add_label(1, 1.22, "[in]")
  add_label(1, 1.09, "[cm]")
  
  plot(vol_red ~ I(vol * 2.54), events_peak_comb[events_peak_comb$soil == "high",], pch = 16, col = 3, las = 1, ylab = "% Volume Reduction", 
       ylim = range_red, xlab = "", xaxt = "n")
  mtext(side = 1, "Storm Depth", line = 3.1, xpd = NA, cex = 0.7)
  add_label(0.85, 0.05, "(b)")
  xvals <- axis(side = 1, mgp = c(2, 0.5, 0))
  axis(side = 1, at = round(xvals / 2.54) * 2.54, labels = round(xvals / 2.54), mgp = c(2, 0.5, 0), line = 1.7)
  add_label(1, 1.22, "[in]")
  add_label(1, 1.09, "[cm]")

  # barplot(vol_high ~ soils + rains, percentages, beside = TRUE, ylab = "% Reduction Runoff Volume Above Threshold", xlab = "", las = 1, col = colors)
  barplot(HPC ~ soil + rain, percentages, beside = TRUE, ylab = "High Pulse Count", xlab = "", las = 1, col = colors)
  add_label(0.85, 0.05, "(c)")
  
  barplot(HPD ~ soil + rain, percentages, beside = TRUE, ylab = "High Pulse Duration (hr)", xlab = "", las = 1, col = colors)
  add_label(0.85, 0.05, "(d)")
  
  barplot(vol_red ~ soil + rain, runoff_combined, beside = TRUE, ylab = "% Surface Runoff Reduction", xlab = "", las = 1, col = colors[2:4])
  add_label(0.85, 0.05, "(e)")
  
  barplot(RBI_daily ~ soil + rain, percentages, beside = TRUE, ylab = "Richards-Baker Index (daily Q)", xlab = "", las = 1, col = colors)
  add_label(0.85, 0.05, "(f)")
  
  # barplot(no_flow ~ soil + rain, percentages, beside = TRUE, ylab = "Duration No Flow (days)", xlab = "", las = 1, col = colors)
  # add_label(0.85, 0.05, "(f)")
  
  mtext("Year", side = 1, line = -0.5, outer = TRUE, cex = 0.8)
  mtext(stringr::str_replace(city, "_", " "), side = 3, line = 1.9, outer = TRUE, font = 2)
  legend("topleft", legend = c("No GI", "High", "Med", "Low"), fill = colors, horiz = TRUE, bty = "n", title = "GI Soil Infiltration",
         inset = c(-0.83, -3), xpd = NA)
  # dev.off()
}

```

<!-- ```{r echo = FALSE, fig.width = 6.5, fig.height = 8} -->
<!--  comb_results2 <- do.call("rbind", comb_results) %>% -->
<!--    mutate(city = factor(city, levels = c("New_Orleans", "Atlanta", "Seattle", "Des_Moines", "Tampa", -->
<!--                                          "Columbus", "Elko", "Los_Angeles", "Colorado_Springs"))) -->

<!--  write.csv(comb_results2, "~/WORK/SWMM_Rain_Gardens/City_Analysis/City_comb_results_basin.csv", row.names = FALSE) -->
<!--   comb_results2 <- read.csv("~/WORK/SWMM_Rain_Gardens/City_Analysis/City_comb_results_basin.csv") %>% -->
<!--    mutate(city = factor(city, levels = c("New_Orleans", "Atlanta", "Seattle", "Des_Moines", "Tampa", -->
<!--                                          "Columbus", "Elko", "Los_Angeles", "Colorado_Springs"))) -->

<!--  colors <- RColorBrewer::brewer.pal(8, "Set1") -->
<!--  colors <- R.utils::insert(colors, ats = c(3, 4), values = adjustcolor(colors[c(2, 3)], alpha.f = 0.6)) -->
<!--  colors <- colors[-8] -->
<!--  colors <- adjustcolor(colors, alpha.f = 0.8) -->
<!--  palette(colors) -->
<!--  png("~/WORK/SWMM_Rain_Gardens/City_Analysis/Cities_Continuous_Summary_basin.png", type = "cairo", units = "in", -->
<!--      height = 8.5, width = 6.5, res = 500) -->
<!--  par(mfcol = c(3, 3), mar = c(4, 3, 1, 0.5), oma = c(5, 1, 2, 1.5), mgp = c(2, 0.8, 0)) -->
<!--  for (i in 1:length(soils)){ -->
<!--    subset <- filter(comb_results2, soil == soils[i]) -->

<!--    plot(HPC_red ~ I(precip * 2.54), subset, pch = 21, bg = subset$city, las = 1, xlab = "", ylab = "", -->
<!--         ylim = c(0, 85), -->
<!--         cex = 1.5, -->
<!--         main = "HPC", xlim = c(0, 203.2), mgp = c(2, 0.5, 0)) -->
<!--    axis(side = 1, at = seq(0, 80, 20) * 2.54, labels = seq(0, 80, 20), line = 1.7, mgp = c(2, 0.5, 0)) -->
<!--    add_label(-0.05, -0.05, paste0("(", letters[i], ")")) -->
<!--    add_label(0.98, 1.19, "[in]") -->
<!--    add_label(0.98, 1.07, "[cm]") -->
<!--    if (i == 1){ -->
<!--      mtext("High Pulse Count % Red.", side = 2, line = 2.7, cex = 0.8) -->
<!--      mtext("Low Infiltration", side = 3, line = 1.2, font = 2) -->
<!--    }else if (i == 2){ -->
<!--      mtext("Med Infiltration", side = 3, line = 1.2, font = 2) -->
<!--    }else { -->
<!--      mtext("High Infiltration", side = 3, line = 1.2, font = 2) -->
<!--    } -->

<!--    plot(HPD_red ~ I(precip * 2.54), subset, pch = 21, bg = subset$city, las = 1, xlab = "", ylab = "", -->
<!--         ylim = range(comb_results2$HPD_red), cex = 1.5, -->
<!--         main = "HPD", xlim = c(0, 203.2), mgp = c(2, 0.5, 0)) -->
<!--    axis(side = 1, at = seq(0, 80, 20) * 2.54, labels = seq(0, 80, 20), line = 1.7, mgp = c(2, 0.5, 0)) -->
<!--    add_label(0.98, 1.19, "[in]") -->
<!--    add_label(0.98, 1.07, "[cm]") -->
<!--    add_label(-0.05, -0.05, paste0("(", letters[i + 3], ")")) -->
<!--    abline(h = 0, lwd = 2) -->
<!--    if (i == 1){ -->
<!--      mtext("High Pulse Duration % Red.", side = 2, line = 2.7, cex = 0.8) -->
<!--    } -->

<!--    plot(vol_red ~ I(precip * 2.54), subset, pch = 21, bg = subset$city, las = 1, xlab = "", ylab = "", -->
<!--         ylim = c(0,85), cex = 1.5, -->
<!--         main = "Surface Runoff", xlim = c(0, 203.2), mgp = c(2, 0.5, 0)) -->
<!--    axis(side = 1, at = seq(0, 80, 20) * 2.54, labels = seq(0, 80, 20), line = 1.7, mgp = c(2, 0.5, 0)) -->
<!--    add_label(0.98, 1.19, "[in]") -->
<!--    add_label(0.98, 1.07, "[cm]") -->
<!--    add_label(-0.05, -0.05, paste0("(", letters[i + 6], ")")) -->
<!--    if (i == 1){ -->
<!--      mtext("Surface Runoff % Red.", side = 2, line = 2.7, cex = 0.8) -->
<!--    } -->

<!--  } -->

<!--  mtext("Total Annual Precipitation", side = 1, outer = TRUE, line = -0.2) -->
<!--  legend("bottomleft", legend = c("New Orleans", "Atlanta", "Seattle", "Des Moines", "Tampa", "Columbus", "Elko", "Los Angeles", "Colorado Springs"), -->
<!--         pch = 21, pt.bg = colors, bty = "n", ncol = 3, inset = c(-1.8, -0.65), xpd = NA, pt.cex = 1.5) -->
<!--  dev.off() -->
<!-- ``` -->

<!-- ```{r echo = FALSE} -->
<!-- #Plot of sub-basin vs. watershed results for continuous sims -->
<!-- # event_results_df <- do.call("rbind", event_results_all) %>% -->
<!-- #   mutate(city = factor(city, levels = c("New_Orleans", "Atlanta", "Seattle", "Des_Moines", "Tampa", -->
<!-- #                                         "Columbus", "Elko", "Los_Angeles", "Colorado_Springs"))) -->
<!-- # -->
<!-- # write.csv(event_results_df, "~/WORK/SWMM_Rain_Gardens/City_Analysis/City_event_results_basin.csv", row.names = FALSE) -->
<!-- event_results_df <- read.csv("~/WORK/SWMM_Rain_Gardens/City_Analysis/City_event_results_basin.csv") %>% -->
<!--   mutate(city = factor(city, levels = c("New_Orleans", "Atlanta", "Seattle", "Des_Moines", "Tampa", -->
<!--                                         "Columbus", "Elko", "Los_Angeles", "Colorado_Springs"))) -->


<!-- source("~/WORK/R Functions/Plot Functions.R") -->

<!-- high_data <- filter(event_results_df, soil == "high") -->
<!-- city_nms <- c("New\nOrleans", "Atlanta", "Seattle", "Des\nMoines", "Tampa", "Columbus", "Elko", "Los\nAngeles", "Colorado\nSprings") -->
<!-- n_events <- group_by(high_data, city) %>% -->
<!--   summarize(n_events = n(), -->
<!--             .groups = "keep") -->

<!-- png("~/WORK/SWMM_Rain_Gardens/City_Analysis/Continous_SubvWatershed_basin.png", type = "cairo", units = "in", width = 6.5, height = 5, res = 500) -->
<!-- par(mfrow = c(2, 1), mar = c(3, 4.5, 1.5, 0.5), mgp = c(2.3, 0.7, 0)) -->
<!-- rodplot(I(sub_peak - peak_red) ~ city, high_data, col = colors, las = 1, main = "Peak Flow", ylab = "Subbasins - Watershed\nPeak % Reduction", -->
<!--         xlab = "", xaxt = "n", ylim = c(-175, 175)) -->
<!-- abline(h = 0, lwd = 2) -->
<!-- axis(side = 1, at = 1:9, labels = city_nms, cex.axis = 0.8, padj = 1, mgp = c(2, -0.1, 0), gap.axis = 0.1) -->
<!-- text("Watershed Effects > Subbasins", x = 10, y = -165, pos = 2, cex = 0.8) -->
<!-- text("Subasin Effects > Watershed", x = 10, y = 165, pos = 2, cex = 0.8) -->
<!-- add_label(-0.02, -0.05, "(a)") -->

<!-- rodplot(I(sub_vol - vol_red) ~ city, high_data, col = colors, las = 1, main = "Runoff Volume", ylab = "Subbasins - Watershed\nVolume % Reduction", -->
<!--         xlab = "", xaxt = "n", ylim = c(-175, 175)) -->
<!-- abline(h = 0, lwd = 2) -->
<!-- axis(side = 1, at = 1:9, labels = city_nms, cex.axis = 0.8, padj = 1, mgp = c(2, -0.1, 0), gap.axis = 0.1) -->
<!-- axis(side = 1, at = 1:9, labels = n_events$n_events, tick = FALSE, line = 1.4, cex.axis = 0.8) -->
<!-- text("# storms =", x = -1, y = -315, pos = 4, cex = 0.8, xpd = NA) -->
<!-- text("Watershed Effects > Subbasins", x = 10, y = -165, pos = 2, cex = 0.8) -->
<!-- text("Subasin Effects > Watershed", x = 10, y = 165, pos = 2, cex = 0.8) -->
<!-- add_label(-0.02, -0.05, "(b)") -->
<!-- dev.off() -->

<!-- ``` -->


```{r echo = FALSE}

GI_event_analysis <- function(city, rain, soil, ratio, hourly_data, dir_name = "C:/Users/lamme1r/Documents/SWMM_bioretention/Sims/Continuous"){

  #Check if .csv file with results already exists, if it does then just read it in, otherwise, create it
  output_file  <- paste0(dir_name, "/", city, "/", city, "_", soil, "_", rain, "_", ratio * 100, "_LID.csv")
  if (file.exists(output_file)){
    lid_ts <- read.csv(output_file)
    #print("Reading saved results from file...")
  }else{
    #print("Writing results to file...")
    #Do event analysis
    index <- which(names(hourly_data) == gsub("_", " ", city))
    events <- event_separation(data = hourly_data[[index]], city = city)

    #Get events for year of analysis
    event_summary <- events[[1]]
    years <- unique(event_summary$year)
    analysis_year <- case_when(rain == "Dry" ~ years[1],
                               rain == "Norm" ~ years[2],
                               rain == "Wet" ~ years[3])

    event_summary <- filter(event_summary, year == analysis_year)

    #Figure out soil porosity based on soil type
    porosity <- case_when(soil == "low" ~ 0.464,
                          soil == "med" ~ 0.463,
                          soil == "high" ~ 0.437)

    #Get GI performance results - Rds file
    file <- paste0(dir_name, "/", city, "/", city, "_", soil, "_", rain, "_", ratio * 100, "_LID.Rds")
    data <- readRDS(file)

    lid_ts <- purrr::map2(data, names(data), function(x, y, event_summary, porosity){
      #x$event[which(x$Date %in% event_summary$start)] <- event_summary$event
      x <- select(x, -event)
      x <- left_join(x, select(event_summary, event, start), by = c("Date" = "start"))
      x$event[1] <- ifelse(is.na(x$event[1]), 1, x$event[1])
      x$event <- zoo::na.locf(x$event)

      data_summary <- x %>%
        group_by(event) %>%
        summarize(inflow = sum(Total_Inflow) * 1 / 60, #inflow in inches
                  evap = sum(Total_Evap) * 1 / 60, #evaporation in inches
                  infil = sum(Surface_Infil) * 1 / 60, #infiltration in inches
                  exfil = sum(Storage_Exfil) * 1 / 60, #exfiltration (into surrounding soils) in inches
                  runoff = sum(Surface_Runoff) * 1 / 60, #surface runoff in inches
                  drain_outflow = sum(Drain_Outflow) * 1 / 60, #Drain outflow in inches
                  outflow = runoff + drain_outflow, #combination of drain outflow and surface runoff in inches
                  outflow_dur = sum(outflow > 0) / 60, #Duration of outflow, in hours
                  max_inflow_rate = max(Total_Inflow), #maximum inflow rate (in/hr)
                  max_inflow_dur = sum(Total_Inflow > Surface_Infil) / 60, #duration above max inflow of rain garden soil (in hours)
                  outflow_high_intensity = sum(Surface_Runoff[Total_Inflow > Surface_Infil & Soil_Moisture < porosity & Storage_Level < 12]) * 1 / 60, #surface outflow caused by too high of rainfall intensity (in inches)
                  max_exfiltration = max(Storage_Exfil), #maximum storage exfiltration rate in in/hr
                  soil_moist_initial = first(Soil_Moisture) / porosity, #inital soil moisture (% saturated)
                  soil_moist_final = last(Soil_Moisture) / porosity, #final soil moisture (% saturated)
                  storage_initial = first(Storage_Level) / 12, #initial storage (% saturated)
                  storage_final = last(Storage_Level) / 12,
                  .groups = "keep")  %>% #final storage (% saturate)
        left_join(event_summary, by = "event") %>%
        mutate(sub = y)

    }, event_summary, porosity)

    lid_ts <- do.call("rbind", lid_ts)

    write.csv(lid_ts, output_file, row.names = FALSE)
  }

  return(lid_ts)
}
```

\newpage

## Green Stormwater Infrastructure Performance
Plots of outflow from of bioretention areas for each city for each of the three years and three soil types simulated. Plots show the percentage of inflow volume, percentage of events, and seasonality of outflow from the bioretention areas associated with high intensity rainfall/runoff and back-to-back storm events.

```{r echo=FALSE, fig.height=7, fig.width=6, warning=FALSE, message=FALSE, fig.align="center", fig.cap=paste0("Outflow from high intensity events (a) and back-to-back events (b) as a percent of inflow, percent of storm events with high intensity outflow (c) and back-to-back outflow (d), and otflow from high intensity events (e) and back-to-back events (f) as a percent of inflow, by season, for ", cities2, ".")}

#Analyze all simulations to get 1) amount of surface runoff from high intensity inflow and 2) fraction of outflow
#that can be attributed to "back-to-back" events
rains <- c("Wet", "Norm", "Dry")
soils <- c("high", "med", "low")
ratios <- 0.1
dir = "C:/Users/lamme1r/Documents/SWMM_bioretention/Sims/Continuous"

results_all <- list()
int_season_all <- list()
sat_season_all <- list()
for (i in 1:length(cities)){
  city <- cities[i]

  results_summary <- list()
  for (j in 1:length(rains)){
    results_summary[[j]] <- list()
    for (k in 1:length(soils)){
        output <- GI_event_analysis(city = city, rain = rains[j], soil = soils[k], ratio = ratios, hourly_data = hourly_data)
        gc()

        #Get sub-basin areas
        inp_file <- read_inp(paste0(dir, "/", city, "/", city, "_", soils[k], "_", rains[j], "_", ratios * 100, ".inp"))
        bioret <- inp_file$lid_usage %>%
          filter(`LID Process` == "BioRet1")
        subbasins <- inp_file$subcatchments

        by_event <- left_join(output, bioret, by = c("sub" = "Subcatchment")) %>%
          group_by(event) %>%
          summarize(tot_outflow = sum(outflow / 12 * Area), #total outflow in ft^3
                    sat_outflow = sum(outflow[soil_moist_initial >= 0.9] / 12 * Area[soil_moist_initial >= 0.9]), #total outflow where initial soil moisture is high
                    int_outflow = sum(outflow[soil_moist_initial < 0.9] / 12 * Area[soil_moist_initial < 0.9]), #total outflow where initial soil moisture is lower
                    tot_inflow = sum(inflow / 12 * Area), #total inflow in ft^3
                    p_depth = mean(vol), #storm depth in inches
                    storm_delta = mean(delta), #time (hours) since previous rainfall event
                    high_intensity_outflow = sum(outflow_high_intensity), #sum of high intensity outflow
                    month = first(lubridate::month(start)), #month of storm event
                    season = case_when(month %in% c(12, 1, 2) ~ "Winter",
                                       month %in% 3:5 ~ "Spring",
                                       month %in% 6:8 ~ "Summer",
                                       month %in% 9:11 ~ "Fall"), #Seasons (meteorolgical)
                    .groups = "keep")
          

        season_results <- by_event %>%
          group_by(season) %>%
          summarize(sat_outflow_sum = sum(sat_outflow),
                    intense_outflow_sum = sum(high_intensity_outflow),
                    .groups = "keep")

        results_summary[[j]][[k]] <- data.frame(surface_runoff = sum(output$runoff),
                                      drain = sum(output$drain_outflow),
                                      tot_runoff = sum(output$outflow),
                                      tot_inflow = sum(output$inflow),
                                      high_intensity_runoff = sum(output$outflow_high_intensity),
                                      tot_outflow_ft3 = sum(by_event$tot_outflow),
                                      sat_outflow_ft3 = sum(by_event$sat_outflow),
                                      n_intense_outflow = sum(by_event$high_intensity_outflow > 0),
                                      n_sat_outflow = sum(by_event$sat_outflow > 0),
                                      n_events = nrow(by_event),
                                      city = city,
                                      rain = rains[j],
                                      soil = soils[k],
                                      ratio = ratios) %>%
                              mutate(frac_high_intensity = high_intensity_runoff / tot_runoff,
                                     frac_intense_events = n_intense_outflow / n_events,
                                     frac_sat = sat_outflow_ft3 / tot_outflow_ft3,
                                     frac_sat_events = n_sat_outflow / n_events,
                                     frac_outflow_tot = tot_runoff / tot_inflow) %>%
          cbind(matrix(unlist(season_results[,2]), ncol = 4, nrow = 1)) %>%
          cbind(matrix(unlist(season_results[,3]), ncol = 4, nrow = 1))

        colnames(results_summary[[j]][[k]])[20:27] <- paste0(c("Fall", "Spring", "Summer", "Winter"), "_", c(rep("sat", 4), rep("intense", 4)))
      }

    }

  results_df <-do.call("rbind", do.call("rbind", results_summary))
  results_all[[i]] <- results_df

  sat_season <- (results_df[,20:23] / results_df$tot_inflow / 95.5) %>%
    mutate(soil = results_df$soil,
           rain = results_df$rain) %>%
    pivot_longer(cols = ends_with("_sat"), names_to = "season", values_to = "sat_perc") %>%
    mutate(season = stringr::str_replace(season, "_sat", ""),
           season = factor(season, levels = c("Winter", "Spring", "Summer", "Fall")),
           city = city)

  int_season <- (results_df[,24:27] / results_df$tot_inflow) %>%
    mutate(soil = results_df$soil,
           rain = results_df$rain) %>%
    pivot_longer(cols = ends_with("_intense"), names_to = "season", values_to = "int_perc") %>%
    mutate(season = stringr::str_replace(season, "_intense", ""),
           season = factor(season, levels = c("Winter", "Spring", "Summer", "Fall")),
           city = city)

  sat_season_all[[i]] <- sat_season
  int_season_all[[i]] <- int_season

  #Plot of intensity and saturation
  # png(paste0("~/WORK/SWMM_Rain_Gardens/City_Analysis/", city, "/", city, "_GI_Summary.png"), type = "cairo", units = "in",
  #     height = 5, width = 5, res = 500)
  colors <- rev(RColorBrewer::brewer.pal(n = 3, "PuBu"))
  palette(colors)
  par(mfcol = c(3, 2), mar = c(3, 4, 1, 0.5), oma = c(1, 0, 3, 0))
  barplot(I(high_intensity_runoff / tot_inflow * 100) ~ soil + rain, results_df, beside = TRUE, ylab = "High Intensity Outflow / Inflow [%]", xlab = "", las = 1,
          col = colors, ylim = c(0, 100))
  add_label(0, 0.05, "(a)")

  barplot(I(frac_intense_events * 100) ~ soil + rain, results_df, beside = TRUE, ylab = "% Events High Intensity Outflow", xlab = "",
          las = 1, col = colors, ylim = c(0, 100))
  add_label(0, 0.05, "(c)")

  beeswarm::beeswarm(I(int_perc * 100) ~ season, int_season, pch = 21, pwbg = int_season$soil, cex = 1.5, las = 1,
                     ylab = "High Intensity Outflow / Inflow [%]",
                     xlab = "", ylim = c(0, 100))
  add_label(0, 0.05, "(e)")

  barplot(I(sat_outflow_ft3 / 95.5 / tot_inflow * 100) ~ soil + rain, results_df, beside = TRUE, ylab = "Back-to-Back Outflow / Inflow [%]", xlab = "", las = 1,
          col = colors, ylim = c(0, 100))
  add_label(0, 0.05, "(b)")

  barplot(I(frac_sat_events * 100) ~ soil + rain, results_df, beside = TRUE, ylab = "% Events Back-to-Back Outflow", xlab = "", las = 1,
          col = colors, ylim = c(0, 100))
  add_label(0, 0.05, "(d)")

  beeswarm::beeswarm(I(sat_perc * 100) ~ season, sat_season, pch = 21, pwbg = sat_season$soil, cex = 1.5, las = 1,
                     ylab = "Back-to-Back Outflow / Inflow [%]",
                     xlab = "", ylim = c(0, 100))
  add_label(0, 0.05, "(f)")

  mtext("Year/Season", side = 1, line = 0, outer = TRUE)
  mtext(stringr::str_replace(city, "_", " "), side = 3, line = 1.9, outer = TRUE, font = 2)
  legend("topleft", legend = c("High", "Med", "Low"), fill = colors, horiz = TRUE, bty = "n", title = "GSI Soil Infiltration",
         inset = c(-0.55, -2.9), xpd = NA)

}
```


<!-- ```{r echo = FALSE} -->
<!-- #Get precip -->
<!-- precip_metrics <- list() -->
<!-- for (i in 1:length(cities)){ -->
<!--   precip_metrics[[i]] <- list() -->
<!--   city <- cities[i] -->
<!--   index <- which(names(hourly_data) == gsub("_", " ", city)) -->
<!--   events <- event_separation(data = hourly_data[[index]], city = city) -->

<!--   #Get events for year of analysis -->
<!--   event_summary <- events[[1]] -->
<!--   years <- unique(event_summary$year) -->

<!--   for (j in 1:length(rains)){ -->
<!--     rain <- rains[j] -->
<!--     analysis_year <- case_when(rain == "Dry" ~ years[1], -->
<!--                                rain == "Norm" ~ years[2], -->
<!--                                rain == "Wet" ~ years[3]) -->

<!--     event_summary2 <- filter(event_summary, year == analysis_year) -->
<!--     events_data <- filter(events[[2]], year == analysis_year) -->

<!--     precip_metrics[[i]][[j]] <- data.frame(delta_mean = mean(event_summary2$delta, na.rm = TRUE), -->
<!--                                            delta_med = median(event_summary2$delta, na.rm = TRUE), -->
<!--                                            dur_mean = mean(event_summary2$dur, na.rm = TRUE), -->
<!--                                            dur_med = median(event_summary2$dur, na.rm = TRUE), -->
<!--                                            int_mean = mean(events_data$value, na.rm = TRUE), -->
<!--                                            int_med = median(events_data$value, na.rm = TRUE), -->
<!--                                            tot_precip = sum(event_summary2$vol, na.rm = TRUE), -->
<!--                                            rain = rain, -->
<!--                                            city = city) -->
<!--   } -->
<!-- } -->

<!-- precip_metrics_df <- do.call("rbind", do.call("rbind", precip_metrics)) -->

<!-- results_all_df <- do.call("rbind", results_all) %>% -->
<!--   mutate(city = factor(city, levels = c("New_Orleans", "Atlanta", "Seattle", "Des_Moines", "Tampa", -->
<!--                                         "Columbus", "Elko", "Los_Angeles", "Colorado_Springs"))) %>% -->
<!--   left_join(precip_metrics_df, by = c("city", "rain")) -->

<!-- # int_season_df <- do.call("rbind", int_season_all) %>% -->
<!-- #     mutate(city = factor(city, levels = c("New_Orleans", "Atlanta", "Seattle", "Des_Moines", "Tampa", -->
<!-- #                                         "Columbus", "Elko", "Los_Angeles", "Colorado_Springs"))) -->
<!-- #  -->
<!-- # sat_season_df <- do.call("rbind", sat_season_all) %>% -->
<!-- #     mutate(city = factor(city, levels = c("New_Orleans", "Atlanta", "Seattle", "Des_Moines", "Tampa", -->
<!-- #                                         "Columbus", "Elko", "Los_Angeles", "Colorado_Springs"))) -->

<!-- write.csv(results_all_df, "../Results/City_GI_results.csv", row.names = FALSE) -->

<!-- colors <- RColorBrewer::brewer.pal(8, "Set1") -->
<!-- colors <- R.utils::insert(colors, ats = c(3, 4), values = adjustcolor(colors[c(2, 3)], alpha.f = 0.6)) -->
<!-- colors <- colors[-8] -->
<!-- colors <- adjustcolor(colors, alpha.f = 0.8) -->
<!-- palette(colors) -->
<!-- soils <- c("low", "med", "high") -->
<!-- png("~/WORK/SWMM_Rain_Gardens/City_Analysis/Cities_GI_Summary2.png", type = "cairo", units = "in", -->
<!--     height = 8.5, width = 6.5, res = 500) -->
<!-- par(mfcol = c(3, 3), mar = c(4.5, 2, 1.5, 1.5), oma = c(3, 1, 2, 1.7), mgp = c(2, 0.5, 0)) -->
<!-- for (i in 1:length(soils)){ -->
<!--   subset <- filter(results_all_df, soil == soils[i]) -->
<!--   # sub_int <- filter(int_season_df, soil == soils[i]) -->
<!--   # sub_sat <- filter(sat_season_df, soil == soils[i]) -->

<!--   # plot(I(tot_runoff / tot_inflow * 100) ~ I(int_mean * 2.54), subset, pch = 21, bg = subset$city, las = 1, xlab = "", ylab = "", -->
<!--   #      ylim = c(0, 100), cex = 1.5, -->
<!--   #      main = "Fraction Outflow") -->
<!--     plot(I(tot_runoff / tot_inflow * 100) ~ I(int_mean * 2.54), subset, pch = 21, bg = subset$city, las = 1, xlab = "", ylab = "", -->
<!--        ylim = c(0, 100), cex = 1.5, -->
<!--        main = "Total Outflow") -->
<!--   axis(side = 1, at = seq(0.04, 0.16, 0.02) * 2.54, labels = seq(0.04, 0.16, 0.02), line = 1.7, mgp = c(2, 0.5, 0)) -->
<!--   add_label(1.01, 1.19, "[in/hr]") -->
<!--   add_label(1.01, 1.07, "[cm/hr]") -->

<!--   add_label(-0.05, -0.05, paste0("(", letters[i], ")")) -->
<!--   if (i == 1){ -->
<!--     mtext("Total Outflow / Inflow [%]", side = 2, line = 1.8, cex = 0.8) -->
<!--     mtext("Low Infiltration", side = 3, line = 1.5, font = 2) -->
<!--   }else if (i == 2){ -->
<!--     mtext("Med Infiltration", side = 3, line = 1.5, font = 2) -->
<!--     mtext("Mean Precip Intensity", side = 1, line = 3.3, cex = 0.8) -->
<!--   }else { -->
<!--     mtext("High Infiltration", side = 3, line = 1.5, font = 2) -->
<!--   } -->

<!--   # plot(I(frac_high_intensity * 100) ~ I(int_mean * 2.54), subset, pch = 21, bg = subset$city, las = 1, xlab = "", ylab = "", -->
<!--   #      ylim = c(0, 100), cex = 1.5, -->
<!--   #      main = "High Intensity") -->
<!--     plot(I(high_intensity_runoff / tot_inflow * 100) ~ I(int_mean * 2.54), subset, pch = 21, bg = subset$city, las = 1, xlab = "", ylab = "", -->
<!--        ylim = c(0, 100), cex = 1.5, -->
<!--        main = "High Intensity") -->
<!--   axis(side = 1, at = seq(0.04, 0.16, 0.02) * 2.54, labels = seq(0.04, 0.16, 0.02), line = 1.7, mgp = c(2, 0.5, 0)) -->
<!--   add_label(1.01, 1.19, "[in/hr]") -->
<!--   add_label(1.01, 1.07, "[cm/hr]") -->

<!--   add_label(-0.05, -0.05, paste0("(", letters[i + 3], ")")) -->
<!--   if (i == 1){ -->
<!--     mtext("High Intensity Outflow / Inflow [%]", side = 2, line = 1.8, cex = 0.8) -->
<!--     #mtext("Low Infiltration", side = 3, line = 1.5, font = 2) -->
<!--   }else if (i == 2){ -->
<!--    # mtext("Med Infiltration", side = 3, line = 1.5, font = 2) -->
<!--     mtext("Mean Precip Intensity", side = 1, line = 3.3, cex = 0.8) -->
<!--   }else { -->
<!--     #mtext("High Infiltration", side = 3, line = 1.5, font = 2) -->
<!--   } -->


<!--   # plot(I(frac_sat * 100) ~ delta_mean, subset, pch = 21, bg = subset$city, las = 1, xlab = "", ylab = "", -->
<!--   #      ylim = c(0, 100), cex = 1.5, -->
<!--   #      main = "Back-to-Back", xaxt= "n") -->
<!--     plot(I(sat_outflow_ft3 / 95.5 / tot_inflow * 100) ~ delta_mean, subset, pch = 21, bg = subset$city, las = 1, xlab = "", ylab = "", -->
<!--        ylim = c(0, 100), cex = 1.5, -->
<!--        main = "Back-to-Back") -->
<!--   axis(side = 1, gap.axis = 0.5) -->
<!--   add_label(-0.05, -0.05, paste0("(", letters[i + 6], ")")) -->
<!--   if (i == 1){ -->
<!--     mtext("Back-to-Back Outflow / Inflow [%]", side = 2, line = 1.8, cex = 0.8) -->
<!--   }else if (i ==2){ -->
<!--     mtext("Mean Time Between Events [hr]", side = 1, line = 2, cex = 0.8) -->
<!--   } -->


<!-- } -->

<!-- legend("bottomleft", legend = c("New Orleans", "Atlanta", "Seattle", "Des Moines", "Tampa", "Columbus", "Elko", "Los Angeles", "Colorado Springs"), -->
<!--        pch = 21, pt.bg = colors, bty = "n", ncol = 3, inset = c(-1.8, -0.5), xpd = NA, pt.cex = 1.5) -->
<!-- dev.off() -->
<!-- ``` -->
