---
# title: "SWMM City Event Analysis"
# author: "Rod Lammers"
# date: "2/10/2020"
output: 
  pdf_document:
    latex_engine: xelatex
mainfont: Arial
header-includes:
  \renewcommand{\thefigure}{S\arabic{figure}}
  \usepackage{float}
  \floatplacement{figure}{H}
  \setcounter{page}{8}
  \setcounter{figure}{4}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Additional Results from Design Storm Simulations

Results from event-scale analysis of GSI scenarios for nine cities from different rainfall regions in the continental US. Individual hydrographs are shown for each rainfall event with lines for different GSI scenarios (bioretention drainage area ratios). Three sets of hydrographs are produced - one for high, medium, and low bioretention soil infiltration rates. Furthermore, performance plots for each city and soil type are included, showing the reductions in peak flows and runoff volumes for the different rainfall events and different GSI scenarios.

```{r echo = FALSE, warning = FALSE, message = FALSE, include = FALSE}
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(zoo))
source("~/WORK/R Functions/Plot Functions.R")
#Get storm values
cities <- c("New_Orleans",
            "Atlanta",
            "Seattle",
            "Des_Moines",
            "Tampa",
            "Elko",
            "Los_Angeles",
            "Columbus",
            "Colorado_Springs")

cities2 <- c("New Orleans",
            "Atlanta",
            "Seattle",
            "Des Moines",
            "Tampa",
            "Elko",
            "Los Angeles",
            "Columbus",
            "Colorado Springs")


#Get 1-month, 6-month, 2-yr, 10-yr, 50-yr, 100-yr for each city
storm_vals <- list()

for (i in 1:length(cities)){
  #Get IDF Curve for city
  IDF <- read.csv(paste0("~/WORK/SWMM_Rain_Gardens/City_Analysis/", cities[i], "_IDF.csv"))
  
  rains <- filter(IDF, Hour == 24) %>%
    select(-Hour)
  
  rains <- rains[1:7]
  
  years <- as.numeric(substr(colnames(rains), 2, nchar(colnames(rains))))
 
  ##Just select frequent rain events as 1/2 and 1/4 of 2-yr event
  storm_vals[[i]] <- unlist(c(rains[1, 2] * c(0.25, 0.5), rains[1, c(2, 4, 6, 7)]))
}  
```

```{r, echo = FALSE, warning = FALSE}
#Functions
plot_hydrographs <- function(results){
  
  suppressMessages(zoo::plot.zoo(results[[1]][[1]][[1]], ylab = "Q [cfs]", las = 1, xlab = "Time", lwd = 3, 
                ylim = c(0, max(results[[1]][[1]][[1]])), col = "black"))
  grid()
  
  colors <- RColorBrewer::brewer.pal(n = length(results), "Greens")
  
  lty <- c(rep(1, 5), 2)
  for (i in 2:length(results)){
    lines(zoo::as.zoo(results[[i]][[1]][[1]]), col = colors[i], lwd = 2, lty = lty[i - 1])
  }
  
  #legend("topright", legend = c("1%", "5%", "10%", "15%", "20%"), col = colors[2:length(colors)], lwd = 2, lty = lty)
  
  #print(max(results[[length(results)]]$Outfall$total_inflow))
}

get_outflow <- function(swmm_files, location = "Outfall"){
  
  # #Get the output discharge at the outfall
  out <- read_out(file = swmm_files, iType = 1, object_name = location,
                  vIndex = 4)
  
  return(out)
  
}

get_report <- function(swmm_files){
  rpt <- read_rpt(swmm_files)
  
  return(rpt[1:4])
}

summarize_results <- function(results, report){
  peaks <- sapply(results, function(x){max(x[[1]][[1]])})
  time <- sapply(results, function(x){which.max(x[[1]][[1]])})
  #vol <- sapply(results, function(x){sum(x$Outfall$total_inflow) * 5 * 60 / 0.94 * 2.59 / 5280 ^ 2 * 12})
  vol <- sapply(report, function(x){
    y <- x$flow_routing_continuity %>%
      filter(Component == "External Outflow")
    return(y$Volume_b) #depth of runoff in 10^6 gal
  })
  
  out <- data.frame(peaks,
                    time,
                    vol,
                    treatment = c("Baseline", "1%", "5%", "10%", "15%", "20%"))
  
  return(out)
}

#Fix subcatchment report
fix_report <- function(y){
  nc <- ncol(y$subcatchment_runoff_summary)
  vals <- apply(y$subcatchment_runoff_summary[,nc], 1, strsplit, "\\s+")
  vals <- t(apply(do.call("rbind", do.call("rbind", vals)), 1, as.numeric))
  #drop column
  y$subcatchment_runoff_summary <- y$subcatchment_runoff_summary[,-nc]
  #Bind
  y$subcatchment_runoff_summary <- cbind(y$subcatchment_runoff_summary, vals)
  #Change names
  colnames(y$subcatchment_runoff_summary) <- c("Subcatchment",
                                               "Total_Precip",
                                               "Total_Runon",
                                               "Total_Evap",
                                               "Total_Infil",
                                               "Imperv_Runoff",
                                               "Perv_Runoff",
                                               "Total_Runoff_Depth",
                                               "Total_Runoff_Volume",
                                               "Total_Peak_Runoff",
                                               "Runoff_Coeff")
  
  return(y)
}

subcatchment_results <- function(ratio, rain, soil, city, dir_name = "C:/Users/rwl21875/Documents/WORK/SWMM_Rain_Gardens/City_Analysis"){
  filenm <- paste0(dir_name, "/", city, "/", "Design_Storms/", city, "_", soil, "_Rainfall_", rain, "_", ratio * 100, ".rpt")
  
  rpt <- read_rpt(filenm)
  rpt <- fix_report(rpt)
  
  input <- read_inp(stringr::str_replace(filenm, "rpt", "inp"))
  baseline_rpt <- fix_report(read_rpt(stringr::str_replace(filenm, paste0(ratio * 100, ".rpt"), "baseline.rpt")))
  
  comb <- left_join(rpt$subcatchment_runoff_summary, input$subcatchments, by = c("Subcatchment" = "Name")) %>%
    left_join(baseline_rpt$subcatchment_runoff_summary, by = "Subcatchment") %>%
    mutate(vol_red = ifelse(Total_Runoff_Depth.y > 0, (Total_Runoff_Depth.y - Total_Runoff_Depth.x) / Total_Runoff_Depth.y * 100, NA),
           peak_red = ifelse(Total_Peak_Runoff.y > 0, (Total_Peak_Runoff.y - Total_Peak_Runoff.x) / Total_Peak_Runoff.y * 100, NA))
  
  summary <- data.frame(cum_vol_red = sum(comb$vol_red * comb$Area, na.rm = TRUE) / sum(comb$Area),
                        cum_peak_red = sum(comb$peak_red * comb$Area, na.rm = TRUE) / sum(comb$Area),
                        ratio = paste0(ratio * 100, "%"),
                        rain = rain,
                        soil = soil,
                        city = city)

 #summary <- data.frame(cum_vol_red = Total_Runoff_Depth.y 
  
  return(summary)
}
```



```{r, echo=FALSE, fig.height = 6, fig.cap="Simulated hydrographs at the watershed outlet for the baseline and GSI scenarios for the 1-month (a), 6-month (b), 2-year (c), 10-yr (d), 50-yr (e), and 100-yr (f) storm events.", warning=FALSE, message=FALSE, fig.align="center"}
source("~/WORK/SWMM_Rain_Gardens/Run SWMM Function.R")

#Plot all hydrographs - also summarize by city
library(swmmr)
rains <- c("1_month", "6_month", "2yr", "10yr", "50yr", "100yr")
soils <- c("low", "med", "high")
ratio <- c(0, 0.01, 0.05, 0.1, 0.15, 0.2)
rain_names <- c("1mo", "6mo", "2yr", "10yr", "50yr", "100yr")

all_cities_summary <- list()
all_cities_summary_ds <- list()
all_cities_subs <- list()
for (i in 1:length(cities)){
#for (i in 1){
  all_cities_summary[[i]] <- list()
  all_cities_summary_ds[[i]] <- list()
  all_cities_subs[[i]] <- list()
  city <- cities[i]
  dir_name <- paste0("C:/Users/rwl21875/Documents/WORK/SWMM_Rain_Gardens/City_Analysis/Design_Storms_NRCS/", city, "/Design_Storms")
  
  results <- list()
  report <- list()
  summary <- list()
  sub_results <- list()
  results_ds <- list()
  summary_ds <- list()
  for (j in 1:length(soils)){
    results[[j]] <- list()
    report[[j]] <- list()
    summary[[j]] <- list()
    sub_results[[j]] <- list()
    results_ds[[j]] <- list()
    summary_ds[[j]] <- list()
    
    for (k in 1:length(rains)){
      files <- lapply(ratio, function(x){list.files(dir_name, pattern = paste0(rains[k], "_", x * 100, ".out"), full.names = TRUE)})
      files[[1]] <- list.files(dir_name, pattern = paste0(rains[k], "_baseline.out"), full.names = TRUE)
      
      #Get only files with the correct soil type
      files <- lapply(files, function(x, soil_type){grep(soil_type, x, value = TRUE)}, soil_type = soils[j])
      
      results[[j]][[k]] <- lapply(files, get_outflow, location = "10yr_Detention")
      results_ds[[j]][[k]] <- lapply(files, get_outflow, location = "J62")
      main_peaks <-  sapply(results[[j]][[k]], function(x){max(x[[1]][[1]])})
      ds_peaks <- sapply(results_ds[[j]][[k]], function(x){max(x[[1]][[1]])})
      
      files <- lapply(ratio, function(x){list.files(dir_name, pattern = paste0(rains[k], "_", x * 100, ".rpt"), full.names = TRUE)})
      files[[1]] <- list.files(dir_name, pattern = paste0(rains[k], "_baseline.rpt"), full.names = TRUE)
      
      #Get only files with the correct soil type
      files <- lapply(files, function(x, soil_type){grep(soil_type, x, value = TRUE)}, soil_type = soils[j])
      
      report[[j]][[k]] <- lapply(files, get_report)
      
      summary[[j]][[k]] <- summarize_results(results[[j]][[k]], report[[j]][[k]])
      summary_ds[[j]][[k]] <- data.frame("In_det" = main_peaks,
                                         "Out_det" = ds_peaks,
                                         "treatment" = c("Baseline", "1%", "5%", "10%", "15%", "20%")) %>%
        mutate(peak_red = (In_det - Out_det) / In_det * 100)
      
      #Get subcatchment-averaged performance and compare to watershed
      # sub_results[[j]][[k]] <- do.call("rbind", lapply(ratio[2:6], subcatchment_results, rain = rains[k], soil = soils[j], city = cities[i],
      #                                                  dir_name = "C:/Users/rwl21875/Documents/WORK/SWMM_Rain_Gardens/City_Analysis/Design_Storms_NRCS"))
    }
    
    #Plot hydrographs
    par(mfrow = c(2, 3), mar = c(4, 4, 2, 0.5), oma = c(0, 0, 2, 0))
    for (k in 1:length(results[[j]])){
      plot_hydrographs(results[[j]][[k]])
      title(main = paste0(rain_names[k], " (", round(storm_vals[[i]][k] * 2.54, 1), " cm/", round(storm_vals[[i]][k], 1), " in)"))
      add_label(-0.08, -0.05, paste0("(", letters[k], ")"))
    }
    mtext(paste(stringr::str_replace(cities[[i]], "_", " "), "-", Hmisc::capitalize(soils[j]), "Infiltration"),
          side = 3, 
          outer = TRUE, line = 0.5, font = 2)
    colors <- RColorBrewer::brewer.pal(n = 6, "Greens")
    legend("topright", legend = c("No GI", "1%", "5%", "10%", "15%", "20%"), col = c("black", colors[2:length(colors)]),
           lwd = 2, bty = "n")
    
    #Plot summary figures
    treat_names = c("Baseline", "1%", "5%", "10%", "15%", "20%")
    summary[[j]] <- purrr::map2(summary[[j]], rains, function(x, y){
      x$Event <- y
      return(x)
    })
    summary_all <- do.call("rbind", summary[[j]]) %>%
      mutate(treatment = factor(treatment, levels = treat_names),
             Event = factor(Event, levels = rains)) %>%
      group_by(Event) %>%
      mutate(peak_red = (peaks[1] - peaks) / peaks[1] * 100,
             time_diff = (time - time[1]) * 5,
             vol_red = (vol[1] - vol) / vol[1] * 100) %>%
      filter(treatment != "Baseline")
    
    summary_ds[[j]] <- purrr::map2(summary_ds[[j]], rains, function(x, y){
      x$Event <- y
      return(x)
    })
    
    summary_all_ds <- do.call("rbind", summary_ds[[j]]) %>%
      mutate(treatment = factor(treatment, levels = treat_names),
             Event = factor(Event, levels = rains)) %>%
      group_by(Event) %>%
      mutate(red_diff = (peak_red[1] - peak_red),
             inflow_diff = In_det[1] - In_det,
             outflow_diff = Out_det[1] - Out_det,
             change = outflow_diff - inflow_diff)
    
    
    # dev.off()
    
    all_cities_summary[[i]][[j]] <- summary_all %>%
      mutate(City = cities[i],
             Soil = soils[j])
    
    all_cities_summary_ds[[i]][[j]] <- summary_all_ds %>%
      mutate(City = cities[i],
             Soil = soils[j])
    
    # all_cities_subs[[i]][[j]] <- do.call("rbind", sub_results[[j]]) %>%
    #   left_join(summary_all, by = c("ratio" = "treatment", "rain" = "Event")) %>%
    #   arrange(desc(rain))
  }
}
  
```
  
```{r, echo = FALSE, fig.height = 8.5, fig.cap=paste0("Reduction in peak flow rate and total runoff volume measured at the watershed outlet for all design storm scenarios for ", cities2, ". Data are shown twice, once as performance vs. storm depth (points colored by DAR; a-c and g-i) and once as performance vs. DAR (points colored by storm depth; d-f and j-l)."), warning=FALSE, message=FALSE, fig.align="center"}  
  colors_ratio <- RColorBrewer::brewer.pal(n = length(treat_names), "Greens")[2:length(treat_names)]
  colors2_ratio <- adjustcolor(colors_ratio, alpha.f = 0.7)
  
  colors_storm <- RColorBrewer::brewer.pal(n = length(rains), "BuPu")
  colors2_storm <- adjustcolor(colors_storm, alpha.f = 0.7)
  palette(colors_storm)
  
  ################################
  #Summary plots
for (i in 1:length(cities)){
#for (i in 1){
  par(mfcol = c(4, 3), mar = c(3.5, 2, 1.5, 0.5), oma = c(3, 1.5, 2.7, 0), mgp = c(2.2, 0.7, 0))
  comb_data <- do.call("rbind", all_cities_summary[[i]])
  ylim_peak <- range(comb_data$peak_red)
  ylim_vol <- range(comb_data$vol_red)
  
  for (j in 1:length(soils)){
    plot(peak_red ~ as.numeric(Event), all_cities_summary[[i]][[j]], pch = 21, bg = colors2_ratio, cex = 1.3,
         las = 1, ylab = "", xlab = "", xaxt = "n", main = "Peak Flow",
         ylim = ylim_peak)
    if (j == 1){
      mtext("% Peak Flow Reduction", side = 2, line = 2.5, cex = 0.7)
    }
    add_label(-0.05, -0.05, paste0("(", letters[j], ")"))
    
    mtext(paste(Hmisc::capitalize(soils[j]), "Infiltration"), side = 3, line = 1.7, font = 2, cex = 0.9)
    axis(side = 1, at = 1:6, labels = rain_names, gap.axis = 0.5)
    treat <- unique(summary_all$treatment)
    for(k in 1:length(treat)){
      sub <- filter(all_cities_summary[[i]][[j]], treatment == treat[k])
      lines(peak_red ~ as.numeric(Event), sub, col = colors2_ratio[k])
    }
    abline(h = 0)
    if (j == 2){
    mtext("Storm Event", side = 1, line = 2, cex = 0.7)
    }
    
    #Plot vs treatment %
    plot(peak_red ~ as.numeric(treatment), all_cities_summary[[i]][[j]], pch = 21, 
         bg = all_cities_summary[[i]][[j]]$Event, cex = 1.3,
     las = 1, ylab = "", xlab = "", xaxt = "n", main = "Peak Flow", ylim = ylim_peak)
    axis(side = 1, at = 2:6, labels = treat_names[2:6])
    add_label(-0.05, -0.05, paste0("(", letters[j + 3], ")"))
    if (j == 1){
      mtext("% Peak Flow Reduction", side = 2, line = 2.5, cex = 0.7)
    }else if (j == 2){
      mtext("Drainage Area Ratio", side = 1, line = 2, cex = 0.7)
    }
    event <- unique(all_cities_summary[[i]][[j]]$Event)
    for(k in 1:length(event)){
      sub <- filter(all_cities_summary[[i]][[j]], Event == event[k])
      lines(peak_red ~ as.numeric(treatment), sub, col = colors2_storm[k])
    }
    abline(h = 0)
    
    
    # plot(time_diff ~ as.numeric(Event), all_cities_summary[[i]][[j]], type = "p", pch = 21, bg = colors2, cex = 1.3,
    #      las = 1, ylab = "", xlab = "", xaxt = "n", main = "Peak Timing",
    #      ylim = ylim_timing)
    # if (j == 1){
    #   mtext("Peak Flow Delay [min]", side = 2, line = 2.5, cex = 0.7)
    # }
    # axis(side = 1, at = 1:6, labels = rains)
    # for(k in 1:length(treat)){
    #   sub <- filter(all_cities_summary[[i]][[j]], treatment == treat[k])
    #   lines(time_diff ~ as.numeric(Event), sub, col = colors2[k])
    # }
    # abline(h = 0)
    
    plot(vol_red ~ as.numeric(Event), all_cities_summary[[i]][[j]], type = "p", pch = 21, 
         bg = colors2_ratio, cex = 1.3,
         las = 1, ylab = "", xlab = "", xaxt = "n", main = "Runoff Volume",
         ylim = ylim_vol)
    add_label(-0.05, -0.05, paste0("(", letters[j + 6], ")"))
    if (j == 1){
      mtext("% Volume Reduction", side = 2, line = 2.5, cex = 0.7)
    }else if(j == 2){
      mtext("Storm Event", side = 1, line = 2, cex = 0.7)
    }

    axis(side = 1, at = 1:6, labels = rain_names, gap.axis = 0.5)
    for(k in 1:length(treat)){
      sub <- filter(all_cities_summary[[i]][[j]], treatment == treat[k])
      lines(vol_red ~ as.numeric(Event), sub, col = colors2_ratio[k])
    }
    abline(h = 0)
    
    plot(vol_red ~ as.numeric(treatment), all_cities_summary[[i]][[j]], type = "p", pch = 21, bg = all_cities_summary[[i]][[j]]$Event, 
         cex = 1.3,
     las = 1, ylab = "", xlab = "", xaxt = "n", main = "Runoff Volume", ylim = ylim_vol)
    axis(side = 1, at = 2:6, labels = treat_names[2:6])
    add_label(-0.05, -0.05, paste0("(", letters[j + 9], ")"))
    if (j == 1){
      mtext("% Volume Reduction", side = 2, line = 2.5, cex = 0.7)
    }else if (j == 2){
      mtext("Drainage Area Ratio", side = 1, line = 2, cex = 0.7)
    }
    for(k in 1:length(event)){
      sub <- filter(all_cities_summary[[i]][[j]], Event == event[k])
      lines(vol_red ~ as.numeric(treatment), sub, col = colors2_storm[k])
    }
    abline(h = 0)

    
  }
  
  mtext(side = 3, text = stringr::str_replace(cities[i], "_", " "), outer = TRUE, font = 2, line = 1.4)
  
    legend("bottomleft", legend = c("1%", "5%", "10%", "15%", "20%"), pt.bg = colors2_ratio, pch = 21, cex = 1, bty = "n",
       title = "Drainage Area Ratio", horiz = TRUE, inset = c(-2.5, -0.7), xpd = NA)
legend("bottomleft", legend = rain_names, 
        pt.bg = cRamp_legend(length(rains), "BuPu", alpha = 0.7), pch = 21, cex = 1, bty = "n", title = "Storm Event",
       horiz = TRUE, inset = c(-0.6, -0.7), xpd = NA)
  
  ##########################
  #Sub-basin vs watershed plots
# 
#   par(mfcol = c(2, 3), mar = c(4, 4, 2, 0.5), oma = c(0, 0, 2.5, 0), mgp = c(2, 0.8, 0))
#   for (j in 1:length(soils)){
#     
#     colors <- adjustcolor(RColorBrewer::brewer.pal(6, "Greens"), alpha.f = 0.7)[2:6]
#     plot(cum_peak_red ~ peak_red, all_cities_subs[[i]][[j]], pch = 21, bg = colors, 
#          cex = as.numeric(all_cities_subs[[i]][[j]]$rain) / 2,
#          xlab = "Watershed % Peak Reduction", ylab = "Subcatchment % Peak Reduction", las = 1,
#          xlim = range(cum_peak_red, peak_red), ylim = range(cum_peak_red, peak_red), main = "Peak Flow")
#     abline(a = 0, b = 1, lwd = 2)
#     mtext(paste(Hmisc::capitalize(soils[j]), "Infiltration Capacity"), side = 3, line = 2, font = 2, cex = 0.9)
#     
#     if (j == 3){
#       legend("bottomright", legend = c("1%", "5%", "10%", "15%", "20%"), pt.bg = colors, pch = 21, bty = "n")
#     }
#     
#     plot(cum_vol_red ~ vol_red, all_cities_subs[[i]][[j]], pch = 21, bg = colors, 
#          cex = as.numeric(all_cities_subs[[i]][[j]]$rain) / 2,
#          xlab = "Watershed % Volume Reduction", ylab = "Subcatchment % Volume Reduction", las = 1,
#          xlim = range(cum_vol_red, vol_red), ylim = range(cum_vol_red, vol_red), main = "Runoff Volume")
#     abline(a = 0, b = 1, lwd = 2)
#     
#     if (j == 3){
#       legend("bottomright", legend = c("1mo", "6mo", "2yr", "10yr", "50yr", "100yr"), pch = 21, pt.bg = colors[5], 
#              pt.cex = 1:6 / 2,
#              bty = "n")
#     }
#     
#   }
#   mtext(side = 3, text = stringr::str_replace(cities[i], "_", " "), outer = TRUE, font = 2, line = 1.5)

}

```


